\chapter{Introduction}\label{chapter:introduction}

The discovery of a Higgs-like boson~\cite{Higgs:1964ia,Higgs:1964pj,Higgs:1966ev,Englert:1964et,Guralnik:1964eu} at CERN in 2012 by the \Gls{ATLAS} and CMS collaborations~\cite{Aad:2012tfa,Chatrchyan:2012xdj} was a major triumph for both theoretical and experimental particle physics.
However, the properties of the new particle remain to be fully verified and the agreement of the predictions of the physics of the Higgs field by the \Gls{Standard Model} (SM) with observations of Nature require further testing.
One important property is the coupling strength of the the Higgs boson to bottom quarks $\left(\Hbb\,\right)$ --- this interaction was only experimentally observed in 2018 through associated production with a vector boson~\cite{Aaboud:2018zhk,CMS:2018abb}.
Additionally, there exist models of particle dark matter~\cite{Abdallah:2015ter} which include massive mediators between dark matter and Standard Model particles.
Such \glspl{dark matter mediator} with couplings to Standard Model quarks would have the same decay signature to pairs of bottom quarks as the Higgs.
This thesis presents a search for high-momentum, low-mass resonances, including the Higgs, in the mass range of $100~\GeV$ to $200~\GeV$ decaying to pairs of $b$-quarks with an associated jet $\left(\jXbb\,\right)$.
The goals of the search are to make a direct measurement of the couplings of Higgs to bottom quarks, and to search for evidence of exotic resonances with couplings to Standard Model quarks.
The thesis proceeds in the following manner.\\

\Cref{chapter:theory} introduces the field theories of the Standard Model, describes the physics of the Higgs field, and motivates the search for couplings of the Higgs to $b$-quarks and the search for exotic low mass resonances.
\Cref{chapter:LHC} introduces CERN's Large Hadron Collider and \Cref{chapter:ATLAS} describes the ATLAS experiment.
\Cref{chapter:bjet_trigger} describes the use of $b$-jet triggers in ATLAS for rapid identification of physics events with $b$-hadrons in the final state.
\Cref{chapter:event_reconstruction} gives an overview of the techniques used by the ATLAS collaboration to reconstruct the signature of particles in the ATLAS detector for physics quality data.
\Cref{chapter:analysis} is devoted to the application of the previous chapters in a search for boosted low mass resonances with a $b\bar{b}$ final state.
The results of this analysis are presented in \Cref{chapter:results}.
\Cref{chapter:software} gives a high level overview of general use statistical analysis software that was developed during the course of the analysis.
Finally, \Cref{chapter:conclusions} provides a summary of the state of measurements of Higgs couplings to heavy flavor quarks and the search for low mass exotic resonances given the results of the search, as well as an outlook to physics in Run 3 of the LHC.
